European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-24 manuscript/manuscript.qmd
drop legitimacy from intro

This paper contributes to the literature in three key ways. First, it offers a direct empirical comparison of US and European influence over IMF lending outcomes—an angle surprisingly overlooked in existing work. Second, by disaggregating “the West” into its US and European components, it uncovers variation in how influence is exercised and to what ends. Third, it challenges the assumption of geographic bias, showing that European powers do not disproportionately favour European borrowers. These findings shed new light on the internal politics of the IMF and speak to wider debates on institutional legitimacy, great power contestation, and the geopolitics of global finance.

@@

>>>>

This paper contributes to the literature in three key ways. First, it offers a direct empirical comparison of US and European influence over IMF lending outcomes—an angle surprisingly overlooked in existing work. Second, by disaggregating “the West” into its US and European components, it uncovers variation in how influence is exercised and to what ends. Third, it challenges the assumption of geographic bias, showing that European powers do not disproportionately favour European borrowers. These findings shed new light on the internal politics of the IMF and speak to wider debates on great power contestation and the geopolitics of global finance.

@@

::: {.data-availability}
**Data Availability Statement**

The replication files for this paper are available at [https://github.com/IMFPaper/IMF](https://github.com/IMFPaper/IMF).
:::

::: {.funding}
**Funding Statement**

This research is not funded.
:::

::: {.competing-interests}
**Competing Interests**

The authors declare none.
:::
